Carbonate chemistry at Ny-Ålesund

### 2023-02-24 awipev-CO2.Rmd
minor commenting
Export latex tables

library("RColorBrewer")
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)
if (!require("pangaear")) install.packages("pangaear")
library("pangaear")
if (!require("latex2exp")) install.packages("latex2exp")
library("latex2exp")
if (!require("gtsummary")) install.packages("gtsummary")
library("gtsummary")
if (!require("todor")) install.packages("todor")
library("todor")
if (!require("ggpmisc")) install.packages("ggpmisc")
library("ggpmisc")
if (!require("tidyselect")) install.packages("tidyselect")
library("tidyselect")
# todor::todor_file("awipev-CO2.Rmd")

@@

@@

# save elements for k1k2 report
k1k2_pco2_at <- list(mean_discrete = mean_discrete, tmp2 = tmp2,
             errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
             diff_ls_quant = diff_ls_quant)
#k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
             # errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
             # diff_ls_quant = diff_ls_quant)
save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")
```

**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

# save elements for k1k2 report
k1k2_at_ct <- list(errors_at_ct = errors_at_ct,
                   diff_table_at_ct = diff_table_at_ct)
save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")
```

>>>>

library("RColorBrewer")
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)
if (!require("pangaear")) install.packages("pangaear")
library("pangaear")
if (!require("latex2exp")) install.packages("latex2exp")
library("latex2exp")
if (!require("gtsummary")) install.packages("gtsummary")
library("gtsummary")
if (!require("todor")) install.packages("todor")
library("todor")
if (!require("ggpmisc")) install.packages("ggpmisc")
library("ggpmisc")
if (!require("tidyselect")) install.packages("tidyselect")
library("tidyselect")
if (!require("usethis")) install.packages("usethis")
library("usethis")
if (!require("ggOceanMaps")) install.packages("ggOceanMaps")
library("ggOceanMaps")

# todor::todor_file("awipev-CO2.Rmd")
#usethis::edit_r_profile()
# to add to .Rprofile file: {.ggOceanMapsenv <- new.env(); .ggOceanMapsenv$datapath <- 'YourCustomPath'}

@@

# ```{r make location map}
# svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
#         legends = FALSE, glaciers = FALSE)
# ggsave(filename = "figures/svalbard_map.png", plot = svalbard_map, width = 25, height = 25, units = "cm")
# ggsave(filename = "figures/svalbard_map.eps", plot = svalbard_map, width = 25, height = 25, units = "cm")
# kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
#         legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
# ggsave(filename = "figures/kong_map.png", plot = kong_map, width = 25, height = 25, units = "cm")
# ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
# ```

@@

# save elements for k1k2 report
k1k2_pco2_at <- list(mean_discrete = mean_discrete, tmp2 = tmp2,
             errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
             diff_ls_quant = diff_ls_quant)
#k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
             # errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
             # diff_ls_quant = diff_ls_quant)
save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")

#export latex table
tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
```
**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

# save elements for k1k2 report
k1k2_at_ct <- list(errors_at_ct = errors_at_ct,
                   diff_table_at_ct = diff_table_at_ct)
save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")

#export latex table
tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
save_kable(file=paste0(tables_path,"diff_table_at_ct"))
```
